### 2023-12-24 sections/4-results.tex
lfd results for sift

% These are going to be boring; saving the interesting discussion for the discussion section

@@

Figure~\ref{fig:results:fashion-mnist-lfd} shows the local fractal dimension by depth for the fashion-mnist dataset. 
We observe that up until depth 5, the LFD at most locations is low, as the 95th percentile (orange plotted line) is less than 4, and the 50th percentile is just above 2.
For depths 15 through 25, we observe that the LFD is higher, as the 95th percentile (orange plotted line) of LFD is slightly less than 6, and the 50th percentile (red plotted line) is near 3.
Finally, for depths 25 through the maximum depth, we observe that the LFD is lower again, as the 95th percentile is between 3 and 4, and the 50th percentile is less than 2.

@@

>>>>

% These are going to be boring; saving the interesting discussion for the discussion section
% I think I should vary the wording more but just getting down the key observations for now

@@

Figure~\ref{fig:results:fashion-mnist-lfd} shows the local fractal dimension by depth for the fashion-mnist dataset. 
We observe that until about depth 5, the LFD at most locations is low, as the 95th percentile (orange plotted line) is less than 4, and the 50th percentile is just above 2.
For depths 15 through 25, we observe that the LFD is higher, as the 95th percentile (orange plotted line) of LFD is slightly less than 6, and the 50th percentile (red plotted line) is near 3.
Finally, for depths 25 through the maximum depth, we observe that the LFD is lower again, as the 95th percentile is between 3 and 4, and the 50th percentile is less than 2.

@@

Figure~\ref{fig:results:sift-lfd} shows the local fractal dimension by depth for the sift dataset. 
Until about depth 5, the 95th percentile is between 2 and 6. From about depth 5 through about depth 20, the 95th percentile is greater than 6, even exceeding 8 near depth 10. 
From about depth 20 onward, the 95th percentile is less than 6, and from about depth 30 onward, it is between 3 and 4. 
The 50th percentile reaches its peak of about 5 at around depth 15, but hovers near 2 after about depth 30.
